Computational Six-bar Synthesis for Implementing Dynamic Behavior

### 2019-03-03 draft.tex
New version according to I-Ming's comments

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{multirow}

@@

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is with the Department of Aerospace and Mechanical Engineering, University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is with the Department of Electrical Engineering and Computer
Sciences, University of California, Berkeley, CA 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received February 3, 2019; revised Month xx, 2019.}}

% The paper headers
\markboth{IEEE Transactions on Robotics,~Vol.~xx, No.~xx, Month~20xx}%
{Plecnik and Fearing: Design Solution for a Stephenson II Timed Path Generator}

@@

\begin{abstract}
Designing a robotic mechanism to perform some desired dynamic behavior under limited actuation power is a challenge.
Descriptions of dynamic requirements inherently exist in the time domain while extant mechanism synthesis techniques are predominantly geometric in nature.
To bridge this gap, we consider the dynamics of a simplified ``mock-up'' model
%of a motor acting through a spring and mechanism to push an inertia.
that excludes mechanism dimensions and topology in place of user-defined kinematic characteristics.
The characteristics that produce the desired dynamic behavior serve as a goal for a to-be-designed mechanism discovered during subsequent kinematic synthesis.
Following this, the synthesis method employed must be capable of sufficiently matching user-defined nonlinearities.
Linkages of the six-bar topology provide this capability but are challenged with design equations of very high degree that have not been solved before.
We solve these equations using the Finite Root Generation technique.
%Our approach is motivated by an application for small legged robots to increase power density through kinematic design rather than actuator sizing.
%While not possible for a directly driven mechanism, we show how this is done using series-elastic actuation.
Our approach is motivated by an application for small legged robots to find a leg mechanism powered by a series elastic actuator capable of recycling a foot path while producing locomotive power within a single stride beyond the actuator's limit.
%While not possible for a directly driven mechanism, we show how this is done using series-elastic actuation.
%We design leg mechanisms capable of continuously recycling a foot path while producing locomotive power within a single stride beyond its actuator's limit.
%Candidate designs are presented that are capable of producing 3.0 times the actuator's power in simulation.
%Experimental results of one such mechanism demonstrated a decrease from the ideal down to 2.6 times the actuator's power.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{here} are no simple tools for designing dynamic machines.
The leading approaches are based in optimization and intuition.
We demonstrate a method that excludes the former and lessens dependence on the latter.
This work is enabled by a new algorithm in numerical homotopy continuation that can find nearly complete solution sets of highly nonlinear systems of equations.
%
The connection to design occurs as these systems of equations comprise geometric design constraints, and their variables are design parameters.
Rather than search through the design space for a set of parameters that satisfy all constraints and minimize some objective, design constraints are posed as systems with isolated roots, where gathering roots is equivalent to compiling candidate design parameters.  The result is a thorough exploration of the design space.

@@

To find an instantiating geometry for a desired mechanical advantage form requires investigation of a sufficiently complex design space capable of satisfying our customization needs.
%Furthermore, configuration-based mechanical advantage must be design simultaneously with desired mechanism configurations.
Luckily, we do not need to consider overly complicated mechanism topologies.
For example, a six-bar linkage, shown in Fig. \ref{intro_sixbar}, is a single degree-of-freedom mechanism.
Despite its simple structure, it is capable of producing complex, constrained motions e.g. it may draw a degree 16 plane curve \cite{primroseSixbarMotionII1967}.
On the other hand, this same simple structure begets challenging nonlinearities within six-bar design equations e.g. the equations investigated in this work are of degree $8.8 \times 10^{12}$.
%On the other hand, despite its simple structure, the design equations associated with six-bar linkages are challenging due to vast nonlinearities in their structure e.g. the equations investigated in this work are of degree xx.
To corral this daunting number, we implement the Finite Root Generation technique \cite{plecnikFindingOnlyFinite2017}, based in numerical homotopy continuation.
This technique estimated the number of finite roots of this system to be around $1.5 \times 10^6$, and found these roots for a numerically general version of the system.
This set of roots itself is a new design instrument, which can be used repeatedly in conjunction with another well established continuation technique \cite{morganCoefficientparameterPolynomialContinuation1989} to efficiently solve systems of this structure.
The equations themselves comprise of the kinematic constraints to coordinate endpoint $P$ with angle $\phi$ of a Stephenson II six-bar linkage, see Fig. \ref{intro_sixbar}.
The complete solution of these equations is first presented in this work.
This solution is particularly useful for synthesizing a point path to coordinate with the mechanical advantage of an input link, albeit indirectly.

@@

In this work, we create a design procedure for instantiating dynamic behavior into a machine by applying FRG to obtain the complete solution of previously unsolved six-bar synthesis equations.
The process begins by posing a simplified system, referred to as a dynamic mock-up, that captures the desired dynamics, presented in Section \ref{sec:dynamic_mock-up}.
The mock-up indicates geometric constraints which are encoded into relevant synthesis equations, presented in Section \ref{sec:synth_eq}.
The FRG method was applied to solve these equations, presented in Section \ref{sec:frg}.
The roots obtained from this solution serve as an instrument to efficiently re-solve the synthesis equations for different geometric requirements.
We demonstrate this in Section \ref{sec:leg_app} by applying the results of FRG to the design of a leg mechanism that modulates power beyond its motors output during a fully rotatable running motion.

@@

In this section, we solve this problem for a Stephenson II six-bar.  The choice to investigate six-bars is not arbitrary.  These linkages are capable of single degree-of-freedom motions which are much more complex than four-bars, the next simplest single degree-of-freedom linkage.  However, the choice to particularly investigate the Stephenson II type of six-bar is partially arbitrary.  There are other types worth investigation too which are not considered in this work.  Before this paper, complete solutions for any type of six-bar timed path generator have not been computed.

Specifically, we formulate the synthesis equations for a Stephenson II six-bar linkage to track an endpoint attached to one of its floating binary links through eight positions that are coordinated with its binary input crank angle.
Later in Section \ref{sec:frg}, these equations are solved for the first time.

@@

Finite Root Generation (FRG) was first proposed in \cite{plecnikFindingOnlyFinite2017}.
The method is based in homotopy continuation and is used for solving kinematic synthesis systems with large numbers of roots.

@@

FRG provides additional computation savings by exploiting known solution structures in a straightforward way.
For linkage synthesis equations, this structure is primarily provided by the presence of linkage cognates.
The cognate of a single degree-of-freedom linkage is another linkage with different dimensions that exactly reproduces some aspect of the original linkage's continuous motion.
For a given linkage type (e.g. Stephenson II) and motion of interest (e.g. timed curve generation), the presence and number of cognates is often known.
As well, geometric transformations between cognates are known too.
Using these transformations, an entire set of cognate roots can be quickly computed from one endpoint.
Each root in a cognate set is a separate isolated solution, and cognate sets have no intersection with each other.
Combining cognate structures with other existing symmetries (if present) partitions target roots into a smaller number of sets, thereby reducing the expected computational load by the multiple of the size of a single solution set.

Finally, any time one intends to solve several systems within a specific family, this is accomplished efficiently using the parameter homotopy method.
That is, in order to solve a new instance of our synthesis system, say for a different set of task parameters, we do not need to start from scratch.
First, all roots are found for a numerically general member of the family of systems of interest.
This is called an \emph{ab initio} solution and may be found using any method, in our case FRG.
The ab initio roots may then serve as startpoints for a homotopy that transforms parameters of the ab initio system into any other member of the family of interest.
These subsequent parameter homotopies only need to track as many paths as the number of roots from the ab initio system, saving computational effort.
Following this strategy, the synthesis system solved below is for ab initio task parameters specified as random complex numbers that do not correspond to anything physical.
In Section \ref{sec:leg_app}, this ab initio solution is used as the start in parameter homotopies for physical relevant target systems.

@@

Unlike other homotopy-based solvers, FRG does not compute roots from a start system generated to match a B\'{e}zout number calculation.
Therefore, rather than moving forward with the formulation of our synthesis system presented in Eqns. (\ref{sub1})--(\ref{sub3}), (\ref{sub6})--(\ref{loopzeta2}), we choose a formulation with fewer equations and unknowns, Eqns. (\ref{loopbeta1})--(\ref{Unorm}).
This formulation is further reduced by substituting $\*U_j = 1/U_j$, $j=1,\ldots,7$ into Eqns. (\ref{loopbeta1})--(\ref{loopzeta1}) to eliminate 7 more variables. 
Although these equations are not polynomial, FRG applies without modification.
We name this system $\mathcal{S}$, its variables $\mathbf{z}$, and its defining parameters $\mathbf{q}$,
\begin{equation}
\mathcal{S}(\mathbf{z},\mathbf{q}) = 0.
\label{system}
\end{equation}
The vector of variables $\mathbf{z}$ contains the unknowns we intend to solve for
\begin{align}
\mathbf{z} = \{ \mathbf{A}, &\mathbf{U} \}, \label{z_variables}\\
\text{where} \quad
\mathbf{A} &= \{ A, B, C, D, F, G, H, \*A, \*B, \*C, \*D, \*F, \*G, \*H \}, \nonumber\\
\mathbf{U} &= \{ U_1, \ldots, U_7 \}. \nonumber
\end{align}
The vector of parameters $\mathbf{q}$ defines the system we are attempting to solve
\begin{align}
\mathbf{q} = \{\mathbf{P}, \*{\mathbf{P}}, &\mathbf{Q}, \*{\mathbf{Q}} \} & & \label{q_parameters}\\
\text{where} \quad
\mathbf{P} &= \{ P_0, \ldots, P_7 \}, & \*{\mathbf{P}} &= \{ \*P_0, \ldots, \*P_7 \}, \nonumber\\
\mathbf{Q} &= \{ Q_1, \ldots, Q_7 \}, & \*{\mathbf{Q}} &= \{ \*Q_1, \ldots, \*Q_7 \}. \nonumber
\end{align}

@@

Unfortunately, Eqns. (\ref{soln_cogns_34_1234}) only apply to cases where corresponding components $Q_j$ and $\*Q_j$ of $\mathbf{q}$ (Eqn. (\ref{q_parameters})) are defined to be reciprocal.
The start systems constructed in Section \ref{sec:start_sys} and the target system constructed for the ab initio solve were defined with $Q_j$ and $\*Q_j$, $j=1,\ldots,7$ as unrelated random complex numbers.
Therefore, only Eqn. (\ref{soln_cogns_12}) applies to them, reducing the size of our cognate sets to two.
Defining $Q_j$ and $\*Q_j$ as reciprocal for start systems was possible, but this increased the numerical precision needed for path tracking such that the cost outweighed the benefit.
With cognate sets of size two, the expected amount of computation is cut in half.
For every finite root found, its cognate partner is readily computed from Eqn. (\ref{soln_cogns_12}).
To find all roots, we only must find all cognate sets, of which there are half as many.

@@

Using the start system construction method of Section \ref{sec:start_sys} and exploiting the cognate structure of Section \ref{sec:cognates}, FRG was applied to find the ab initio roots $\mathbf{z}$ of a numerically general target system $\mathcal{S}(\mathbf{z},\mathbf{q}_1)=0$.
Target parameters $\mathbf{q}_1$ were randomly generated and are printed in Appendix \ref{app:fpm}.
After generating this ab initio solution, these roots can be used repeatedly in conjunction  with the parameter homotopy method to solve for any other system $\mathcal{S}(\mathbf{z},\mathbf{q}_2)=0$, where $\mathbf{q}_2$ might be defined by a specific synthesis task.
In Section \ref{sec:leg_app}, we will define $\mathbf{q}_2$ according to analyses in Section \ref{sec:dynamic_mock-up}, to design a novel machine.

@@

FRG was written in CUDA and run on a laptop GPU for 3,563,520 trials over 24 hours.
It found 764,894 distinct cognate sets indicating 1,529,788 finite roots.
Of these, 1180 roots were suspected of being singular due to high condition numbers and so were discarded, leaving 1,528,608 isolated solutions.
According to the FRG estimation technique, this is 99.0\% of roots.  About 0.14\% of paths ended in numerical failure, usually from the Newton corrector step not converging due to precision limitations.  Fig. \ref{frg_results} displays root accumulation over FRG iterations.  The diminishing returns of FRG is documented in \cite{plecnikStudyFindingFinite2017}.  We estimate the algorithm would have found 99.9\% of roots with $1.77\times 10^6$ more trials.

@@

The ab initio implementation of FRG presented in Section~\ref{sec:computations} found nearly all finite roots for a numerically general system $\mathcal{S}(\mathbf{z},\mathbf{q}_1)=0$.
This root set can be used to efficiently solve systems of the form $\mathcal{S}$ henceforth.
Parameter homotopies can be constructed that use these roots as startpoints to track to the roots of some other systems of the form $\mathcal{S}(\mathbf{z},\mathbf{q}_2)=0$.
However, the vector of parameters $\mathbf{q}$ (defined in Eqn. (\ref{q_parameters})) for these systems were composed of physical specifications informed by the analysis of Section \ref{sec:dynamic_mock-up}.

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{multirow}
\usepackage[dvipsnames]{xcolor}

@@

\title{Designing Dynamic Machines \\ With Large Scale Root Finding}

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is with the Department of Aerospace and Mechanical Engineering, University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is with the Department of Electrical Engineering and Computer
Sciences, University of California, Berkeley, CA 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received March 3, 2019; revised Month xx, 2019.}}

% The paper headers
\markboth{IEEE Transactions on Robotics,~Vol.~xx, No.~xx, Month~20xx}%
{Plecnik and Fearing: Designing Dynamic Machines With Large Scale Root Finding}

@@

\begin{abstract}
%Designing a robotic mechanism to perform some desired dynamic behavior under limited actuation power is a challenge.
%Descriptions of dynamic requirements inherently exist in the time domain while extant mechanism synthesis techniques are predominantly geometric in nature.
%To bridge this gap, we consider the dynamics of a simplified ``mock-up'' model
%that excludes mechanism dimensions and topology in place of user-defined kinematic characteristics.
%The characteristics that produce the desired dynamic behavior serve as a goal for a to-be-designed mechanism discovered during subsequent kinematic synthesis.
%Following this, the synthesis method employed must be capable of sufficiently matching user-defined nonlinearities.
%Linkages of the six-bar topology provide this capability but are challenged with design equations of very high degree that have not been solved before.
%We solve these equations using the Finite Root Generation technique.
%Our approach is motivated by an application for small legged robots to find a leg mechanism powered by a series elastic actuator capable of recycling a foot path while producing locomotive power within a single stride beyond the actuator's limit.

%Computational tools based in homotopy continuation have enabled a new design technique for dynamic machines.  In the past, mechanism design was commonly accomplished by optimization algorithms working under kinematic requirements.  Our work does not build off those foundations, but instead demonstrates the utility of the recently developed Finite Root Generation (FRG) technique by delineating a technique for designing under dynamic requirements.   The key characteristic of FRG compared to other algorithms is its ability to find a nearly complete solution set to mechanism design equations that are prohibitively burdened with numerous roots at infinity.  In turns out, most mechanism topologies that include a floating closed kinematic are prohibitively burdened with infinite roots such that their complete set of solutions have never been found (for brevity, we call these equations unsolved).  An example of unsolved design equations comes from the Stephenson II six-bar, a simple-looking planar linkage.  Its timed curve design equations are solved for the first time here due to the algorithmic advantages of FRG.  This work on planar six-bars is not only immediately useful, as demonstrated by a robotic leg prototype, but provides solid foundations for generalizing into spatial mechanisms with floating closed chains.

Endowing a robot with a desired dynamic behavior through careful design of its morphology presents a motivating challenge.  
Past work largely employs optimization to perform design.  This work does not build off those foundations.  
Choosing an objective function and searching for a global optimum in an intensely nonlinear design space is difficult, especially if stochastic seeding is involved.  
This paper takes an entirely different approach.  Optimization is not considered.  
Design requirements are encoded into a square system of equations that manifests the design space's nonlinearities.  
Due to these nonlinearities, a system of these sorts will possess a huge number of isolated roots.  
{\color{ForestGreen}
Each root contains a description of robot geometry, so that their discovery becomes the action of design.  
Following this, the computation of all isolated roots constitutes design space exploration.  
In contrast to optimal synthesis, the role of design exploration is to survey a multitude of solutions over the entirety of the design space.
Optimal synthesis is a different activity that searches for the minimum of an objective function.
}
However, computing all isolated roots to a massively nonlinear system is not a routine task.  
It turns out the systems we are interested in are heavily burdened with infinite roots, a type of degenerate root, resulting in a small percentage of physically relevant roots.  
A recently developed algorithm termed Finite Root Generation relieves this burden. It has enabled the computation of all isolated roots to systems that were not possible in the past.  
Some readers may find the structures surprisingly simple of the mechanical systems from which previously not all isolated roots could be computed.  
In this paper, we obtain all isolated roots for a certain six-bar design problem for the first time.  
{\color{ForestGreen}
This set of roots, which could not be computed in the past, enables the design of a transmission function over the path of a mechanism's end effector such that desired dynamic behaviors can be instantiated.  
Six-bar motions offer a level of complexity that make this topology particular viable.  
The result is an unprecedented design exploration procedure for machines that exhibit a desired dynamic behavior.  
}
This work on planar six-bars is not only immediately useful, as demonstrated by a robotic leg prototype, but provides solid foundations for generalizing into spatial mechanisms.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{here} are no simple tools for designing machines to exhibit some desired dynamic behavior.
The leading approaches are based in optimization and intuition.
In this work, we exclude the former and lessen dependence on the latter.
We propose a scheme for design space exploration powered by the recent Finite Root Generation (FRG) algorithm \cite{plecnikFindingOnlyFinite2017}, a method for obtaining all isolated roots to a system of equations.
FRG is able to obtain complete sets of roots for systems of equations that were computationally prohibitive in the past.
In this work, we identify one such system particularly useful for designing dynamic machines.
It is related to a planar six-bar linkage with transmission properties specified along its end effector path.
Since all isolated roots to this related system were not obtainable in the past, the design exploration procedure we present in this work surpasses the capabilities of previous synthesis methods.

This work is unrelated to conventional methods based in optimization.
For given robot dimensions, software tools such as rigid body dynamics solvers already exist to analyze dynamic behavior.  Pairing these with black box optimizers forms an update loop between design parameters (robot dimensions) and the resulting behavior.  This approach to design leads to methods just a varied as the underlying optimizers.  Once a meaningful objective function is established, global optimums are sought, but are challenged by design space nonlinearities.

This work takes entirely different approach.
Design requirements are translated into a system of equations.
This system exhibits intense nonlinearities.
However, the algorithms of numerical homotopy continuation are well equipped (perhaps the most equipped) to handle these nonlinearities.
By formulating synthesis systems to be square, its roots become isolated.
These roots might be imagined as a spread of points across the design space.
Each of these points indicates a portion of the design space where requirements are met.
Therefore, the action of obtaining all roots constitutes design space exploration.
{\color{ForestGreen}
FRG is able to obtain 99.0\% of candidate design points.
}
Locating these points through a high dimensional grid search in a nonlinear space is computationally prohibitive.
However, in practice, synthesis systems are riddled with infinite roots, a type of degenerate root which is physically irrelevant.
This is where current homotopy root-finding algorithms fall short.  
It is often the case that upwards of 95\% of computations are dedicated to discovering useless roots at infinity.

A notable contribution toward alleviating the burden of infinite roots was the introduction of regeneration homotopy by Hauenstein et al. \cite{hauensteinRegenerationHomotopiesSolving2011}
Their method was applied to a system of degree 264,241,152.
In this work, we consider a system of degree $8.8\times 10^{12}$.  
Through FRG, we find that only 0.000017\% of roots are finite.  
The rest are physically useless.
The contribution of FRG was to eliminate all computations related to infinite roots.
The motivation was to be able to obtain all isolated solutions to systems with degrees greater than ever before.
In this work, we are finding all isolated roots for one such system, and demonstrating new design capabilities offered by that power.  
As the design work conducted in this paper is on a planar six-bar linkage, it may be surprising to some readers that not all isolated roots of all planar linkages were found in the past.
Perhaps even more surprising, the frontier of this knowledge begins as soon as one deviates from the simple four-bar linkage.
The reason these computations have not taken place in the past is the overwhelming presence of infinite roots in the synthesis equations.  These calculations have remained computationally prohibitive even with tremendous growth in computer speeds and parallelization.  FRG approaches this challenge from the algorithm level.
{\color{ForestGreen}
This paper lays the groundwork for generalizations into more complex spatial linkages.  
In the past, it has been shown how planar modules can lead to complex spatial chains \cite{plecnikControllingMovementTRR2016}.
}

From the standpoint of new design capabilities, by finding all isolated roots to a six-bar linkage that prescribes a transmission function over the path of its end effector, we are able to perform design exploration for machines that explicitly prescribes torque/force ratios between the actuator and load at different points of the configuration space.
Control over these force ratios gives us control over dynamic behavior.  Performing design exploration over these dynamic machines gives us an unprecedented design tool.

%\IEEEPARstart{A}{} new design technique for dynamic machines has been made possible by a recent algorithm in numerical homotopy continuation.  This is not related to past work in kinematic synthesis that finds single solutions through optimization.  Instead we are interested in design exploration, which compiles multiple design candidates over the entirety of the design space.  The enabling feature of our work is to find complete solution sets to design equations which are heavily burdened with infinite roots.  This is related to other techniques that find complete solutions to polynomial systems [cite], of which numerical homotopy continuation solvers indisputably solve the biggest.  Our work is distinguished by solving\footnote{By use of the word ``solve'', we mean to find numerical approximations to all solutions for a single system of equations.  We often deal with solution sets in the millions.  This is different from solving for one or two solutions.} the largest systems to date.  The size of a polynomial system is a complex topic that necessarily requires some measure of degree, of which there are several [cite].  For the design equations of interest, these calculations lead to huge overestimations of the number of finite roots of a system.  From the standpoint of a homotopy solver, the difference between these estimations and the finite root set represents a prohibitively large number of roots at infinity to compute.  With this in mind, the degree of a system best measures its computational barrier to entry and gives very little bearing on the maximum number of design solutions which might be found.  Our contribution is to algorithmically lower this barrier to entry with the Finite Root Generation (FRG) method [cite].  To demonstrate, we solve a set of design equations that has never been solved$^1$ in the past: timed curve generation for a planar six-bar linkage.  It may come as a surprise to some readers that these equations were not solved$^1$ long ago.  It turns out the burden of infinite roots prevented this until now.  It is often the case that mechanism topologies, planar or spatial, which include a floating closed loop suffer from this affliction.  In order to drive towards more complicated spatial designs, we recognize the importance of due diligence in the plane.  Furthermore, we demonstrate the immediate utility of the six-bar topology by designing a dynamic leg mechanism for a robot.
%
%There are no simple tools for designing dynamic machines.
%The leading approaches are based in optimization and intuition.
%Our method excludes the former and lessens dependence on the latter.
%Our work is enabled by the recent Finite Root Generation (FRG) algorithm, which can obtain all isolated roots of highly nonlinear systems of equations.
%%
%The connection to design occurs as these systems of equations comprise geometric design constraints, and their variables are design parameters.
%Rather than search through the design space for a set of parameters that satisfy all constraints and minimize some objective, design constraints are posed as systems with isolated roots, where gathering roots is equivalent to compiling candidate design parameters.  The result is a thorough exploration of the design space.

@@

To find an instantiating geometry for a desired mechanical advantage form requires investigation of a sufficiently complex design space capable of satisfying our customization needs.
%Furthermore, configuration-based mechanical advantage must be design simultaneously with desired mechanism configurations.
Luckily, we do not need to consider overly complicated mechanism topologies.
For example, a six-bar linkage, shown in Fig. \ref{intro_sixbar}, is a single degree-of-freedom mechanism.
Despite its simple structure, it is capable of producing complex, constrained motions e.g. it may draw a degree 16 plane curve \cite{primroseSixbarMotionII1967}.
On the other hand, this same simple structure begets challenging nonlinearities within six-bar design equations e.g. the equations investigated in this work are of degree $8.8 \times 10^{12}$.
%On the other hand, despite its simple structure, the design equations associated with six-bar linkages are challenging due to vast nonlinearities in their structure e.g. the equations investigated in this work are of degree xx.
To corral this daunting number, we implement the Finite Root Generation technique \cite{plecnikFindingOnlyFinite2017}, based in numerical homotopy continuation.
This technique estimated the number of finite roots of this system to be around $1.5 \times 10^6$, and found these roots for a numerically general version of the system.
This set of roots itself is a new design instrument, which can be used repeatedly in conjunction with another well established continuation technique \cite{morganCoefficientparameterPolynomialContinuation1989} to efficiently find the isolated roots of any system of this structure.
The equations themselves comprise of the kinematic constraints to coordinate endpoint $P$ with angle $\phi$ of a Stephenson II six-bar linkage, see Fig. \ref{intro_sixbar}.
The complete set of isolated roots of these equations is first presented in this work.
This set of roots is particularly useful for synthesizing a point path to coordinate with the mechanical advantage of an input link, albeit indirectly.
{\color{ForestGreen}
We are performing design space exploration by finding nearly all isolated roots, something that was not possible on this scale in the past.
In particular, we are able to perform design exploration for machines with control over the ratios between input torque and load.  This gives us control over dynamic behavior.
Since these sets of isolated roots were only recently computable by FRG, we present a design exploration tool for dynamic machines that was not possible in the past.
}

@@

In this work, we create a design procedure for instantiating dynamic behavior into a machine by applying FRG to obtain the all isolated roots of a system that was previously computationally prohibitive.
The process begins by posing a simplified system, referred to as a dynamic mock-up, that captures the desired dynamics, presented in Section \ref{sec:dynamic_mock-up}.
The mock-up indicates geometric constraints which are encoded into relevant synthesis equations, presented in Section \ref{sec:synth_eq}.
The FRG method was applied to obtain all isolated roots of these equations, presented in Section \ref{sec:frg}.
These roots serve as an design instrument to efficiently obtain all roots of the synthesis equations for different geometric requirements.
We demonstrate this in Section \ref{sec:leg_app} by applying the results of FRG to the design of a leg mechanism that modulates power beyond its motors output during a fully rotatable running motion.

@@

In this section, formulate synthesis equations for a Stephenson II six-bar and compute all of its isolated roots.  The choice to investigate six-bars is not arbitrary.  These linkages are capable of single degree-of-freedom motions which are much more complex than four-bars, the next simplest single degree-of-freedom linkage.  However, the choice to particularly investigate the Stephenson II type of six-bar is partially arbitrary.  There are other types worth investigation too which are not considered in this work.  Before this paper, complete sets of isolated roots for any type of six-bar timed path generator have not been computed.

Specifically, we formulate the synthesis equations for a Stephenson II six-bar linkage to track an endpoint attached to one of its floating binary links through eight positions that are coordinated with its binary input crank angle.
Later in Section \ref{sec:frg}, all isolated roots of these equations are obtained for the first time.

@@

Finite Root Generation (FRG) was first proposed in \cite{plecnikFindingOnlyFinite2017}.
The method is based in homotopy continuation and is used for obtaining all isolated roots to large kinematic synthesis systems.

@@

FRG provides additional computation savings by exploiting known solution structures in a straightforward way.
For linkage synthesis equations, this structure is primarily provided by the presence of linkage cognates.
The cognate of a single degree-of-freedom linkage is another linkage with different dimensions that exactly reproduces some aspect of the original linkage's continuous motion.
For a given linkage type (e.g. Stephenson II) and motion of interest (e.g. timed curve generation), the presence and number of cognates is often known.
As well, geometric transformations between cognates are known too.
Using these transformations, an entire set of cognate roots can be quickly computed from one endpoint.
Each root in a cognate set is a separate isolated solution, and cognate sets have no intersection with each other.
Combining cognate structures with other existing symmetries (if present) partitions target roots into a smaller number of sets, thereby reducing the expected computational load by the multiple of the size of a single cognate root set.

Finally, any time one intends to obtain all isolated roots for several systems within a specific family, this is accomplished efficiently using the parameter homotopy method.
That is, in order to obtain a complete set of isolated roots for a new instance of our synthesis system, say for a different set of task parameters, we do not need to start from scratch.
First, all roots are found for a numerically general member of the family of systems of interest.
This is called an \emph{ab initio} solution and may be found using any method, in our case FRG.
The ab initio roots may then serve as startpoints for a homotopy that transforms parameters of the ab initio system into any other member of the family of interest.
These subsequent parameter homotopies only need to track as many paths as the number of roots from the ab initio system, saving computational effort.
Following this strategy, the synthesis system below from which we obtain all roots is for ab initio task parameters specified as random complex numbers that do not correspond to anything physical.
In Section \ref{sec:leg_app}, this ab initio solution is used as the start in parameter homotopies for physical relevant target systems.

@@

Unlike other homotopy-based root-finders, FRG does not compute roots from a start system generated to match a B\'{e}zout number calculation.
Therefore, rather than moving forward with the formulation of our synthesis system presented in Eqns. (\ref{sub1})--(\ref{sub3}), (\ref{sub6})--(\ref{loopzeta2}), we choose a formulation with fewer equations and unknowns, Eqns. (\ref{loopbeta1})--(\ref{Unorm}).
This formulation is further reduced by substituting $\*U_j = 1/U_j$, $j=1,\ldots,7$ into Eqns. (\ref{loopbeta1})--(\ref{loopzeta1}) to eliminate 7 more variables. 
Although these equations are not polynomial, FRG applies without modification.
We name this system $\mathcal{S}$, its variables $\mathbf{z}$, and its defining parameters $\mathbf{q}$,
\begin{equation}
\mathcal{S}(\mathbf{z},\mathbf{q}) = 0.
\label{system}
\end{equation}
The vector of variables $\mathbf{z}$ contains the unknowns we intend to solve for
\begin{align}
\mathbf{z} = \{ \mathbf{A}, &\mathbf{U} \}, \label{z_variables}\\
\text{where} \quad
\mathbf{A} &= \{ A, B, C, D, F, G, H, \*A, \*B, \*C, \*D, \*F, \*G, \*H \}, \nonumber\\
\mathbf{U} &= \{ U_1, \ldots, U_7 \}. \nonumber
\end{align}
The vector of parameters $\mathbf{q}$ defines the system we are attempting to solve
\begin{align}
\mathbf{q} = \{\mathbf{P}, \*{\mathbf{P}}, &\mathbf{Q}, \*{\mathbf{Q}} \} & & \label{q_parameters}\\
\text{where} \quad
\mathbf{P} &= \{ P_0, \ldots, P_7 \}, & \*{\mathbf{P}} &= \{ \*P_0, \ldots, \*P_7 \}, \nonumber\\
\mathbf{Q} &= \{ Q_1, \ldots, Q_7 \}, & \*{\mathbf{Q}} &= \{ \*Q_1, \ldots, \*Q_7 \}. \nonumber
\end{align}

@@

Unfortunately, Eqns. (\ref{soln_cogns_34_1234}) only apply to cases where corresponding components $Q_j$ and $\*Q_j$ of $\mathbf{q}$ (Eqn. (\ref{q_parameters})) are defined to be reciprocal.
The start systems constructed in Section \ref{sec:start_sys} and the target system constructed for the ab initio system were defined with $Q_j$ and $\*Q_j$, $j=1,\ldots,7$ as unrelated random complex numbers.
Therefore, only Eqn. (\ref{soln_cogns_12}) applies to them, reducing the size of our cognate sets to two.
Defining $Q_j$ and $\*Q_j$ as reciprocal for start systems was possible, but this increased the numerical precision needed for path tracking such that the cost outweighed the benefit.
With cognate sets of size two, the expected amount of computation is cut in half.
For every finite root found, its cognate partner is readily computed from Eqn. (\ref{soln_cogns_12}).
To find all roots, we only must find all cognate sets, of which there are half as many.

@@

Using the start system construction method of Section \ref{sec:start_sys} and exploiting the cognate structure of Section \ref{sec:cognates}, FRG was applied to find the ab initio roots $\mathbf{z}$ of a numerically general target system $\mathcal{S}(\mathbf{z},\mathbf{q}_1)=0$.
Target parameters $\mathbf{q}_1$ were randomly generated and are printed in Appendix \ref{app:fpm}.
After generating this ab initio solution, these roots can be used repeatedly in conjunction  with the parameter homotopy method to obtain all isolated roots for any other system $\mathcal{S}(\mathbf{z},\mathbf{q}_2)=0$, where $\mathbf{q}_2$ might be defined by a specific synthesis task.
In Section \ref{sec:leg_app}, we will define $\mathbf{q}_2$ according to analyses in Section \ref{sec:dynamic_mock-up}, to design a novel machine.

@@

FRG was written in CUDA and run on a laptop GPU for 3,563,520 trials over 24 hours.
It found 764,894 distinct cognate sets indicating 1,529,788 finite roots.
Of these, 1180 roots were suspected of being singular due to high condition numbers and so were discarded, leaving 1,528,608 isolated roots.
According to the FRG estimation technique, this is 99.0\% of roots.  About 0.14\% of paths ended in numerical failure, usually from the Newton corrector step not converging due to precision limitations.  Fig. \ref{frg_results} displays root accumulation over FRG iterations.  The diminishing returns of FRG is documented in \cite{plecnikStudyFindingFinite2017}.  We estimate the algorithm would have found 99.9\% of roots with $1.77\times 10^6$ more trials.

@@

The ab initio implementation of FRG presented in Section~\ref{sec:computations} found nearly all finite roots for a numerically general system $\mathcal{S}(\mathbf{z},\mathbf{q}_1)=0$.
This root set can be used to efficiently obtain all isolated roots for systems of the form $\mathcal{S}$ henceforth.
Parameter homotopies can be constructed that use these roots as startpoints to track to the roots of some other systems of the form $\mathcal{S}(\mathbf{z},\mathbf{q}_2)=0$.
However, the vector of parameters $\mathbf{q}$ (defined in Eqn. (\ref{q_parameters})) for these systems were composed of physical specifications informed by the analysis of Section \ref{sec:dynamic_mock-up}.
